\sectionTitle{Professional Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
\experience
{Present}{Admissions Ambassador}{Undergraduate Admissions Office}{Caltech, Pasadena, CA}
{April 2019} {
\begin{itemize}
\item Design and lead campus tours, student panels, and social blogs to prospective students, families, teachers, faculty, counselors, and alumni.
\item Run the front desk of the Caltech Admissions office.
\end{itemize}
}
{Social Outreach, Management, Communication, Writing}
\emptySeparator
\experience
{March 2020}{Undergraduate Assignment}{Division of Physics, Mathematics \& Astronomy}{Caltech, Pasadena, CA}
{January 2020} {
\begin{itemize}
\item Designed and managed websites for courses in math and physics.
\item Implemented web-scrappers to automate the archiving of old assignment data, course listings, and department webpages.
\item Wrote email marketing and managed listings for the physics and math department.
\end{itemize}
}
{Web Development, Python, Management, Communication, Social Outreach}
\emptySeparator

\experience
{January 2020}{Undergraduate Assignment}{Fellowships and Study Abroad Office}{Caltech, Pasadena, CA}
{October 2019} {
\begin{itemize}
\item Facilitated communication with about 6 partner universities and created outreach materials for several exchange and fellowship programs.
\item Managed the course listings, webpages, office, and library of the Caltech FASA program.
\end{itemize}
}
{Management, Communication, Writing}
\emptySeparator

\experience
{September 2017}{Developer}{Indian Institute of Technology, Delhi}{New Delhi, India}
{January 2017} {
\website{https://drive.google.com/file/d/1fBpIIc-LXF_BZ8OCRdhghjH0INn3hPUe/view?usp=sharing}{Abstract \& Certification} \website{https://www.vlab.co.in/}{Virtual Labs}
\begin{itemize}
\item Worked on the end-user testing of the \href{https://vlabs.co.in/}{Virtual Labs} project, run by the Government of India, that addresses the lack of good lab facilities and trained
teachers, by allowing remote experimentation.
\item Responsible for development of 3 virtual labs, each with about 10 experiments, in satellite modeling and simulation, astrophysics, instrumentation, \& communications. 
\end{itemize}
}
{Social Outreach, Python, Web Development}
\emptySeparator


\end{experiences}
