\sectionTitle{Projects}{\faLaptop}
\begin{projects}
\project
{Dwaar Lucknow}{2017 - 2020}
{\website{https://drive.google.com/file/d/1zHBGNWfpEnw6O0Fz3oO6AsF00uPr4RXu/view}{Abstract} \website{http://dwaarlucknow.weebly.com/}{dwaarlucknow}}
{\begin{itemize}
\item Co-founded and ran a non-profit initiative that connects people to credible social help organizations. Connected with over \textit{20 national non-profit}s and generated an \textit{outreach of nearly 50,000} through our 25 partners.
\item Created a novel system for a geographically based social petition platform, which was recognized by the \textbf{Indian Institute of Technology at Kanpur} as one of the national best student ideas at its collegiate competitions.
\item Co-developed a website and Android application featured on radio and in newspapers.
\end{itemize}
}
{Non-Profit, Management, Website Development, Android, Social Outreach}

\project{LAMINA: Using Multiple Coronagraphs for High Contrast Imaging and Spectroscopy}{2021}{\website{https://docs.google.com/presentation/d/1Gzx4t5RMjlNy5Zm4jH3gldLti_w3IcNC8NMAvKq0Ovg/edit#slide=id.gfc9fdbc362_5_0}{Slides}}
{Developed the science case and co-designed an outline for a multiplexed instrument concept for high contrast imaging, as submission for the NYRIA2021 workshop hackathon.}
{Direct Imaging}

\end{projects}
\begin{projects}

\project{Quantum Hack Microsoft Challenge: Grover's Algorithm}{2021}{\github{shubhagrawal30/qchack-microsoft-challenge}}
{Implemented quantum oracles to be used with Grover's algorithm to solve a range of classical problems. Selected from about 80 projects to be a presenter at the closing proceedings of the conference.}
{Quantum Algorithms}

\project{Fast Quantum Hamiltonian Compilation}{2020}{\github{gianelgado12/cs101-Fast-Hamiltonian-Project}}
{Analyzed the complexity of two methods of quantum hamiltonian compilation: First Order Trotter Suzuki and qDRIFT.}
{Quantum Algorithms}

\end{projects}